Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-07-21 mu/article/article.tex
Corrections before review with BMS.

We calculated the self-consistent ground state and the Kohn-Sham
states using density functional theory in the local density approximation (DFT-
LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
% 
We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
Gaussian pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit
interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
in Eq. \eqref{eq:mu}.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{Up} and \emph{Alt} structures are cutoff energies of 40\,Ha and
65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
respectively. The energy eigenvalues and matrix elements for the \emph{Up} and
\emph{Alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ and
$\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron method
(LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
$\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the crystal potential, in
$\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give small contribution
to PSC.\cite{bhatPRL05} Therefore, $[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1}
reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$.

@@

\begin{table}[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{Up}    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  684.2    \\
             &      &       & 1.954  & $\mathrm{yz}$ &  293.9    \\
             &      &       & 1.958  & $\mathrm{yz}$ & -273.0    \\
\emph{Alt}   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -722.2    \\
             &      &       & 0.911  & $\mathrm{yz}$ & -357.8    \\
 CdSe        & bulk & 90    & 0.912  & $\mathrm{zz}$ &  -32.3    \\
 GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -29.9    \\
\hline
\end{tabular}

@@

Using  Eq. \eqref{eq:vab-aw}, we calculated 
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and
\emph{Alt} 2D structures and for CdSe and GaAs which are bulk systems; 
the results
are presented in Fig. \ref{fig:vab-str-comp}. 
The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
The most intense response corresponds to the \emph{Alt} structure centered at
0.720\,eV corresponding to the short-wavelength infrared radiation (SWIR) and
reaching a $\calv^{\rmy\rmz}=-722.2$ Km/s, which means the electrons moving
along $y$ (parallel to the surface) with the spin polarized along $z$
(perpendicular to the surface), with a speed of -722.2 Km/s.
% 
For an energy range from 0.66\,eV to 3.0\,eV, corresponding to energies of the
Near Infrared (NIR) to visible radiation (VIS), the \emph{Up} structure has two
peaks centered at 1.954\,eV and 1.958\,eV reaching $\calv^{\rmy\rmz}=293.9$
Km/s and $\calv^{\rmy\rmz}=-273.0$ Km/s and the \emph{Alt} structure one more
peak centered at 0.0.911\,eV reaching $\calv^{\rmy\rmz}=-357.83$ Km/s.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.912\,eV reaching $\calv^{\rmz\rmz}=-32.3$ Km/s, and the
GaAs structure response reaches the maximum centered at 2.326\,eV reaching
$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=--28.9$ Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of these values for
the 2D and bulk structures; a positive (negative) spin-velocity means that the
velocity moves (anti-)parallel to the electric field.
% 
We remark that the 2D structures have resonances that give larger values for
$\calv^{\rma\rmb}$ than the bulk crystals; in particular the \emph{Alt}
structure is $\sim 22$ times more intense.

@@

We present in Figs. \ref{fig:up-vsz-w1} and \ref{fig:up-vsz-w2}
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ for the two energy ranges
of the \emph{Up} structure that give the highest values for $\calv^{\rmy\rmz}$
shown in Fig.~\ref{fig:vab-str-comp}.
% 
We obtain that the zone where the maximum response is reached corresponds to a
energy range of the incident beam from 0.084\,eV to 0.093\,eV, corresponding to
the LWIR, and polarization angles $\alpha$ between $35^{\circ}$ and
$55^{\circ}$. Also,  two local maxima are held for same $\ga$ between
$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.950\,eV and
1.960\,eV, in the VIS range.
% %%%%%%%%%%%%%%%%% 
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%

In bottom panel of Fig. \ref{fig:up-vsz-w1} we first analyze the response for
$\hbar\go= 0.084$ eV which gives the maximum. We show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\ga$
(left scale, black solid line). The absolute maximum is obtained when $\alpha =
35^{\circ}$ resulting in a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 758.2$\,Km/s, that according to Eq.~\eqref{eq:vs-mag} comes
from $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 326.7$\,Km/s and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha) = 684.2$\,Km/s.
% 
In the same panel we present the corresponding velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red line), that for the
absolute maximum at $\ga = 35^\circ$ is $\gamma_{\mathrm{z}}(\hbar\omega =
0.084\text{eV},\alpha = 35^\circ) = 64.475^{\circ}$. This results means that at
$\hbar\go=0.084$ eV and a polarization angle of the incoming electric field of
$\ga = 35^\circ$ the electrons with a spin pointing along $z$ move at angle of
$\gamma_{\mathrm{z}}(\hbar\omega = 0.084\text{eV},\alpha=35^\circ) \sim
64.5^{\circ}$ with respect to the $x$ direction, with a  maximum speed
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  758.2 Km/s. Also, from
Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.475^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 646.0$ Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.47^\circ$, gives
$\ga=154.47^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
195.6$ Km/s (see blue arrow); thus, for $\hbar\go=0.084$ eV, an $\alpha \sim
65.47^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
along $z$ moving parallel (perpendicular) to the incident electric field,  with
a speed of 646.0 (195.6) Km/s.
% 
We also find that for all values of $\ga$, $\gamma_{\mathrm{z}}(\omega,\alpha)
\sim 64.48^{\circ}$, being almost constant, and 180.0 Km/s
$<\calv_{\gs^z}(\go,\ga)<$ 758.2 Km/s.

In the bottom panel of Fig. \ref{fig:up-vsz-w2}, now we take
$\hbar\go=1.954$ eV which is the local maximum 
shown in the to panel of same figure. 
The local maximum is
again at  $\alpha = 35^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
300.4$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
78.0^{\circ}$.
% 
In this case, $\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =183.7$
Km/s (green circled box and arrow), and
$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.0^{\circ}$, for $\alpha =168.0^
{\circ}$ (blue squared box and arrow).
% 
We find  that the velocity angle is almost constant having a range from
$77^{\circ}$ to $78.04^{\circ}$ for  $0^{\circ} \leq
\alpha \leq 180^{\circ}$, and 6.8 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 300.4 Km/s.
% 
Although no figures are presented, we also made the analysis for the
cases when the spin polarization is directed 
along $\mathrm{x}$ and $\mathrm{y}$, finding 
the maxima for
$\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
$\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
$\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In bottom panel of Fig. \ref{fig:alt-vsz} we plot $\calv_{\gs^z}(\go,\ga)$ vs.
$\ga$ (left scale, black line), fixing the energy to 0.720 eV. The absolute
maximum is obtained for $\alpha = 150^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.5$ Km/s.
% 
In the same panel we present the velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red line), that for
the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 108.9^{\circ}$.
% 
Also, the green circle indicates the value of $\ga$ for which the electrons
move parallel to the incoming electric field, i.e. $\alpha =
\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 108.7^{\circ}$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 511.3$ Km/s. Likewise, the
blue circle indicates the value of $\ga$ for which the electrons move
perpendicular to the incoming electric field, i.e. $\alpha=19.8^{\circ}$, with
$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=109.8^{\circ}$, and
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=61.5$ Km/s.
% 
We also have that $\gamma_{\mathrm{z}}(\omega,\alpha)$ is centered at
$109.1^{\circ}$ having variations of $\pm 0.9^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
the maximum values are $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) =
297.8$ Km/s and $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$
Km/s, corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.2^{\circ}$ and both for
$\alpha=145^{\circ}$, where the plots are not presented.

@@

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
%     \\
%     \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
%     \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
%     $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
%     photon energy and polarization angle $\alpha$ for the \emph{Up} structure.
%     The absolute maxima of both are localized in the energy range from 0.08\,eV
%     to 0.10\,eV, in the Far  Infrared, and for polarization angles from
%     $25^{\circ}$ to $50^{\circ}$.}
%     \label{fig:up-3d-vva-1}
% \end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vx-vy-w1}
    \caption{caption here}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%% 
We proceed to analyze the \emph{Up} structure for the case when the velocity is
directed along the $x$ and $y$ coordinates. We found that each response has a
maximum for $\hbar\omega=0.084$ eV, in the LWIR, and $\ga=35^{\circ}$.
% 
Fixing $\ga=35^{\circ}$, in Fig. \ref{fig:up-vab-comp-rtp-1} we plot
$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$ (left scale, black
line) where each responses has a maximum of 442.4\,Km/s and 705.5\,Km/s,
respectively, for $\hbar\go=0.084$ eV.
% 
We also present the corresponding polar (right scale, red line) and azimuthal
(right scale, blue dashed line) spin polarization angles that have values of
% 
$\theta_{\mathrm{x}}(\omega,\alpha) = 42.4^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.1^{\circ}$ 
% 
when the  electron moves along $x$, and  
$\theta_{\mathrm{y}}(\omega,\alpha) = 14.1^{\circ}$, and
$\varphi_{\mathrm{y}} (\omega,\alpha) = 81.4^{\circ}$, 
% 
when the electron moves along $y$. This means that, the spin is directed upward
the third Cartesian quadrant of the $xy$ plane when the electron moves along
$x$, and is directed almost perpendicularly over the $xy$ plane when it moves
along $y$.
% 
Also, from this figure we have that when the electron moves along $x$ the spin
direction is almost constant for all the energies across the peak of the
response, having a ranges of
% 
$42.4^{\circ} < \theta_{\mathrm{x}}(\omega,\alpha) < 53.6^{\circ} $ 
and $208.1^{\circ} < \varphi_{\mathrm{x}} (\omega,\alpha) < 215.8^{\circ}$. 
% 
Then, when the electron moves along $y$ the spin's polar angle has again
small variations,
% 
$7.6^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) < 14.1^{\circ}$, 
% 
but in contrast with this the azimuthal angle has significant variations,
% 
$81.4^{\circ} < \varphi_{\mathrm{y}} (\omega,\alpha) < 150.7^{\circ}$.

>>>>

We calculated the self-consistent ground state and the Kohn-Sham
states using density functional theory in the local density approximation 
(DFT-LDA) with a planewave basis using the ABINIT code \cite{gonzeCPC09}.
% 
We used Hartwigsen-Goedecker-Hutter (HGH) relativistic separable dual-space
Gaussian pseudopotentials \cite{hartwigsenPRB98} including the spin-orbit
interaction needed to calculate $\mu^{\mathrm{abcd}}(\omega,\alpha)$ presented
in Eq. \eqref{eq:mu}.
% 
The convergence parameters for the calculations of our results corresponding to
the \emph{Up} and \emph{Alt} structures are cutoff energies of 40\,Ha and
65\,Ha, resulting in LDA energy band gaps of 0.084\,eV and 0.718\,eV,
respectively. The energy eigenvalues and matrix elements for the \emph{Up} and
\emph{Alt} structures were calculated using 12802 $\mathbf{k}$ points and 14452
$\mathbf{k}$ points in the IBZ to integrate $\mu^{\mathrm{abcd}}(\go)$ and
$\xi^{\rma\rmb}(\go)$ using the linearized analytic tetrahedron method
(LATM).\cite{nastosPRB07} We neglect the anomalous velocity term
$\hbar(\bfgs\times\nabla V)/4m^2c^2$, where $V$ is the crystal potential, in
$\hat\bfv$ of Eq.~\eqref{z.1}, as this term is known to give small contribution
to PSC.\cite{bhatPRL05} Therefore, $[\hat\bfv,\hat\bfS]=0$ and Eq.~\eqref{z.1}
reduces to $\hat K^{\rma\rmb}=\hat v^\rma \hat S^\rmb=\hat S^\rmb \hat v^\rma$.

@@

\begin{table}[b]
\begin{tabular}{cccccc}
\hline
\multirow{2}{*}{Structure \quad} & 
Kind of \quad & 
Pol. &
Energy & 
\multicolumn{2}{c}{$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$}\\
\cline{5-6}
& system & Ang. & [eV] & $\mathrm{ab}$ \quad & [Km/s]\\
\hline
\emph{Up}    & 2D   & 35    & 0.084  & $\mathrm{yz}$ &  684.2    \\
             &      &       & 1.954  & $\mathrm{yz}$ &  293.9    \\
             &      &       & 1.958  & $\mathrm{yz}$ & -273.0    \\
\emph{Alt}   & 2D   & 150   & 0.720  & $\mathrm{yz}$ & -722.2    \\
             &      &       & 0.911  & $\mathrm{yz}$ & -351.7    \\
 CdSe        & bulk & 90    & 0.912  & $\mathrm{zz}$ &  -32.3    \\
 GaAs        & bulk & 90    & 2.326  & $\mathrm{xx}$ &  -28.9    \\
\hline
\end{tabular}

@@

Using  Eq. \eqref{eq:vab-aw}, we calculated
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ for the \emph{Up} and \emph{Alt} 2D
structures and for CdSe and GaAs which are bulk systems; the results are
presented in Fig. \ref{fig:vab-str-comp}. The polarization angle of the
incoming beam, $\alpha$, presented in the response of each structure is that
for which the response is maximized in each case.
% 
The most intense response corresponds to the \emph{Alt} structure centered at
0.720\,eV corresponding to the short-wavelength infrared radiation (SWIR) and
reaching a $\calv^{\rmy\rmz}=-722.2$ Km/s, which means the electrons moving
along $y$ (parallel to the surface) with the spin polarized along $z$
(perpendicular to the surface), with a speed of -722.2 Km/s.
% 
For an energy range from 0.66\,eV to 3.0\,eV, corresponding to energies of the
Near Infrared (NIR) to visible radiation (VIS), the \emph{Up} structure has two
peaks centered at 1.954\,eV and 1.958\,eV reaching $\calv^{\rmy\rmz}=293.9$
Km/s and $\calv^{\rmy\rmz}=-273.0$ Km/s and the \emph{Alt} structure one more
peak centered at 0.911\,eV reaching $\calv^{\rmy\rmz}=-351.7$ Km/s.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.912\,eV reaching $\calv^{\rmz\rmz}=-32.3$ Km/s, and the
GaAs structure response reaches the maximum centered at 2.326\,eV reaching
$\calv^{\rmx\rmx}=\calv^{\rmy\rmy}=-28.9$ Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of these values for
the 2D and bulk structures; a positive (negative) spin-velocity means that the
velocity moves (anti-)parallel to the electric field.
% 
We remark that the 2D structures have resonances that give larger values for
$\calv^{\rma\rmb}$ than the bulk crystals; in particular the \emph{Alt}
structure is $\sim 22$ times more intense.

@@

We present in Figs. \ref{fig:up-vsz-w1} and \ref{fig:up-vsz-w2}
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ for the two energy ranges
of the \emph{Up} structure that give the highest values for $\calv^{\rmy\rmz}$
shown in Fig.~\ref{fig:vab-str-comp}.
% 
We obtain that the zone where the maximum response is reached corresponds to a
energy range of the incident beam from 0.084\,eV to 0.093\,eV, corresponding to
the LWIR, and polarization angles $\alpha$ between $35^{\circ}$ and
$55^{\circ}$. Also,  two local maxima are held for same $\ga$ between
$35^{\circ}$ and $55^{\circ}$, but for an energy range between 1.952\,eV and
1.960\,eV, in the VIS range.
% %%%%%%%%%%%%%%%%% 
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%

In bottom panel of Fig. \ref{fig:up-vsz-w1} we first analyze the response for
$\hbar\go= 0.084$ eV which gives the maximum. We show
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ as a function of $\ga$
(left scale, black line). The absolute maximum is obtained when $\alpha =
35^{\circ}$ resulting in a value of $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 758.2$\,Km/s, that according to Eq.~\eqref{eq:vs-mag} comes
from $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha) = 326.7$\,Km/s and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha) = 684.2$\,Km/s.
% 
In the same panel we present the corresponding velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ (right scale, red line), that for the
absolute maximum at $\ga = 35^\circ$ is $\gamma_{\mathrm{z}}(\hbar\omega =
0.084\text{eV},\alpha = 35^\circ) = 64.47^{\circ}$. This results means that at
$\hbar\go=0.084$ eV and a polarization angle of the incoming electric field of
$\ga = 35^\circ$ the electrons with a spin pointing along $z$ move at angle of
$\gamma_{\mathrm{z}}(\hbar\omega = 0.084\text{eV},\alpha=35^\circ) \sim
64.5^{\circ}$ with respect to the $x$ direction, with a  maximum speed
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)$ of  758.2 Km/s. Also, from
Eq. \eqref{eq:gamma-par} we find that
$\gamma^\parallel_{\mathrm{z}}(\omega,\alpha)=\ga=64.47^\circ$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 646.0$ Km/s (see green
arrow), and that from Eq. \eqref{eq:gamma-perp},
$\gamma^\perp_{\mathrm{z}}(\omega,\alpha)=\ga-90^\circ=64.47^\circ$, gives
$\ga=154.47^\circ$, with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) =
195.6$ Km/s (see blue arrow); thus, for $\hbar\go=0.084$ eV, an $\alpha \sim
65.5^\circ$ ($\alpha \sim 154.5^\circ$) gives electrons with spin polarized
along $z$ moving parallel (perpendicular) to the incident electric field,  with
a speed of 646.0 (195.6) Km/s.
% 
We also find that for all values of $\ga$, $\gamma_{\mathrm{z}}(\omega,\alpha)
\sim 64.48^{\circ}$, being almost constant, and 180.0 Km/s
$<\calv_{\gs^z}(\go,\ga)<$ 758.2 Km/s.

In the bottom panel of Fig. \ref{fig:up-vsz-w2}, now we take
$\hbar\go=1.954$ eV which gives the local maximum 
shown in the to panel of same figure. 
The local maximum is
again at  $\alpha = 35^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) =
300.4$ Km/s and $\gamma_{\mathrm{z}}(\omega,\alpha) =
78.0^{\circ}$.
% 
In this case, $\alpha =\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) =
78.0^{\circ}$ with $\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 187.6$
Km/s (green circled box and arrow), and
$\gamma_{\mathrm{z}}^\perp(\omega,\alpha) = 78.0^{\circ}$, for $\alpha =168.0^
{\circ}$ (blue squared box and arrow) with $\mathcal{V}_{\sigma^{\mathrm{z}}}
(\omega,\alpha) = 92.4$.
% 
We find  that the velocity angle is almost constant having a range from
$77^{\circ}$ to $78.04^{\circ}$ for  $0^{\circ} \leq
\alpha \leq 180^{\circ}$, and 6.8 Km/s $<\calv_{\gs^z}(\go,\ga)<$ 300.4 Km/s.
% 
Although no figures are presented, we also made the analysis for the
cases when the spin polarization is directed 
along $\mathrm{x}$ and $\mathrm{y}$, finding 
the maxima for
$\hbar\go=0.084$ eV and $\alpha=35^{\circ}$, with
$\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)=219.6$ Km/s and
$\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)=280.3$ Km/s,
$\gamma_{\mathrm{x}}(\omega,\alpha) = 79.3^{\circ}$, and 
$\gamma_{\mathrm{y}}(\omega,\alpha) = 78.2^{\circ}$.

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
In bottom panel of Fig. \ref{fig:alt-vsz} we plot $\calv_{\gs^z}(\go,\ga)$ vs.
$\ga$ (left scale, black line), fixing the energy to 0.720 eV. The absolute
maximum is obtained for $\alpha = 150^{\circ}$ with
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha) = 763.6$ Km/s.
% 
In the same panel we present the velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ vs $\ga$ (right scale, red line), that for
the absolute maximum is $\gamma_{\mathrm{z}}(\omega,\alpha) = 108.9^{\circ}$.
% 
Also, the green circle indicates the value of $\ga$ for which the electrons
move parallel to the incoming electric field, i.e. $\alpha =
\gamma_{\mathrm{z}}^\parallel(\omega,\alpha) = 108.7^{\circ}$, with
$\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha) = 538.5$ Km/s. Likewise, the
blue circle indicates the value of $\ga$ for which the electrons move
perpendicular to the incoming electric field, i.e. $\alpha=19.8^{\circ}$, with
$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=109.8^{\circ}$, and
$\mathcal{V}_{\sigma^{\mathrm{z}}} (\omega,\alpha)=61.5$ Km/s.
% 
We also have that $\gamma_{\mathrm{z}}(\omega,\alpha)$ is centered at
$109.1^{\circ}$ having variations of $\pm 0.9^{\circ}$ for $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
Again, for the cases in which the spin polarization is parallel to the surface
the maximum values are $\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha) =
297.8$ Km/s and $\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha) = 606.4$
Km/s, corresponding to $\gamma_{\mathrm{x}}(\omega,\alpha) = 116.3^{\circ}$
$\gamma_{\mathrm{y}}(\omega,\alpha) = 110.1^{\circ}$ and both for
$\alpha=150^{\circ}$, where the plots are not presented.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vx-vy-w1}
    \caption{caption here}
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%% 
We proceed to analyze the \emph{Up} structure for the case when the velocity is
directed along the $x$ and $y$ coordinates. We found that each response has a
maximum for $\hbar\omega=0.084$ eV, in the LWIR, and $\ga=35^{\circ}$.
% 
Fixing $\ga=35^{\circ}$, in Fig. \ref{fig:up-vab-comp-rtp-1} we plot
$\mathcal{V}^{\mathrm{x}} (\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{y}}(\omega,\alpha)$ vs. $\hbar\go$ (left scale, black
line) where each responses has a maximum of 442.4\,Km/s and 705.5\,Km/s,
respectively, for $\hbar\go=0.084$ eV.
% 
We also present the corresponding polar (right scale, red line) and azimuthal
(right scale, blue line) spin polarization angles that have values of
% 
$\theta_{\mathrm{x}}(\omega,\alpha) = 42.4^{\circ}$, and
$\varphi_{\mathrm{x}}(\omega,\alpha) = 208.1^{\circ}$ 
% 
when the  electron moves along $x$, and  
$\theta_{\mathrm{y}}(\omega,\alpha) = 14.1^{\circ}$, and
$\varphi_{\mathrm{y}} (\omega,\alpha) = 81.4^{\circ}$, 
% 
when the electron moves along $y$. This means that, the spin is directed upward
the third Cartesian quadrant of the $xy$ plane when the electron moves along
$x$, and is directed almost parallel to the $xy$ plane in the first quadrant
when it moves along $y$.
% 
Also, from this figure we have that when the electron moves along $x$ the spin
direction is almost constant for all the energies across the peak of the
response, having a ranges of
% 
$42.4^{\circ} < \theta_{\mathrm{x}}(\omega,\alpha) < 53.6^{\circ} $ 
and $208.1^{\circ} < \varphi_{\mathrm{x}} (\omega,\alpha) < 215.8^{\circ}$. 
% 
Then, when the electron moves along $y$ the spin's polar angle has again
small variations,
% 
$7.6^{\circ} < \theta_{\mathrm{y}} (\omega,\alpha) < 14.1^{\circ}$, 
% 
but in contrast with this the azimuthal angle has significant variations,
% 
$81.4^{\circ} < \varphi_{\mathrm{y}} (\omega,\alpha) < 150.7^{\circ}$.

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vx-vy-w2}
    \caption{Caption here}
    \label{fig:up-vx-vy-w2}
\end{figure}
% %%%%%%%%%%%%%%%%%
% %% 1.80 eV - 2.10 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
In  Fig. \ref{fig:up-vx-vy-w2}, for the \emph{Up} structure, we plot
$\mathcal{V}^{\mathrm{a}} (\omega,\alpha)$ vs. $\go$, fixing
$\alpha=35^{\circ}$; the range of $\go$ lies in part of the VIS range. We see
that there are two local maxima at $\hbar\go=1.954$ eV and $\hbar\go=1.958$ eV.
For the first that is the most intense we obtain
% 
$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) =  93.9$ Km/s and  
$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 456.3$ Km/s.
% 
For these local maxima, the corresponding polar and azimuthal spin polarization
angles are
% 
$\theta_{\mathrm{x}} (\omega,\alpha) = 48.5^{\circ}$, and 
$\varphi_{\mathrm{x}} (\omega,\alpha) = 54.4^{\circ}$,
% 
for the electron moving along $x$, and
% 
$\theta_{\mathrm{y}} (\omega,\alpha) = 49.9^{\circ}$, and 
$\varphi_{\mathrm{y}} (\omega,\alpha) = 51.8^{\circ}$
% 
for the electron moving along $y$. We remark that these angles are almost
constant for all the energy values across the peak of this local maxima, for
which the spin is directed upward in the first Cartesian quadrant of the $xy$
plane when it moves along either $x$ or $y$ directions. 
% 
For the $\hbar\go=1.958$\,eV peak we obtain 
$\theta_{\mathrm{x}} (\omega,\alpha) = 129.9^{\circ}$, and 
$\varphi_{\mathrm{x}} (\omega,\alpha) = 231.6^{\circ}$, with 
$\mathcal{V}^{\mathrm{x}} (\omega,\alpha) = 88.8$ Km/s, and
% 
$\theta_{\mathrm{y}}(\omega,\alpha) =129.3$, and
$\varphi_{\mathrm{y}}(\omega,\alpha) = 230.4$, with 
$\mathcal{V}^{\mathrm{y}} (\omega,\alpha) = 431.4$ Km/s. 
% 
Again, for this local maxima, the spin angles are almost constant across the
resonant peak directed for both cases downward the third quadrant of the $xy$
plane.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% Res: fixin vel Alt  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
